Flexibility of interactions depends on habitat suitability

### 2019-06-12 paper/manuscript.Rmd
Add line to remind me to get topography data
First draft cleaning species methods

---
title: "Flexibility of interactions depends on habitat suitability"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: 
  - bibliography.bib
  - int-bibliography.bib
csl: pnas.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

@@

We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014] on`r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")` (Figure \@ref(fig:fig-worldmap)). 
Some studies included interaction data recorded at multiple points in time. 
When this was the case, we combined them into one single interaction network per location. 
All together, these networks included

@@

>>>>

---
title: "Flexibility of interactions depends on habitat suitability"
author: 
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
bibliography: 
  - bibliography.bib
  - int-bibliography.bib
csl: pnas.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
editor_options: 
  chunk_output_type: console
---

@@

We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014] on`r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")` (Figure \@ref(fig:fig-worldmap)). 
This database contains datasets originating from XX studies published in the primary literature between XX and XX. 
Before assessing how habitat suitability affects interaction partners of plants and pollinators we need to link species across different datasets. 
However, this task is complicated by the inacurracies often found in diverse data sources. 
Most commonly, there are typos in the species names, species names have bee abbreviated or a single species might be recorded as different synonyms in different sources. 
To alleviate this issue we restored to the following procedure.

First, to

Some studies included interaction data recorded at multiple points in time. 
When this was the case, we combined them into one single interaction network per location. 
All together, these networks included

@@

See topography data from Species distribution model transferability and model grain size – finer may not always be better
